Over-relaxed Sinkhorn's Algorithm for Regularized Optimal Transport

### 2017-10-10 paper.tex
Suite corrections

\subsection{Over-relaxed projections}

@@

\begin{lemma}
	\label{lemma:trivial_intersection}
	Let us take $\gamma^0$ in $\IR_{+*}^{n_1 n_2}$,
	and denote
	\[
	S = \left\{
	\diag(a) \gamma^0 \diag(b),\quad
	(a,b) \in \IR_{+*}^{n_1 + n_2}
	\right\}
	\]
	the set of matrices that are diagonally similar to $\gamma^0$.
	Then the set $S \cap \Ccal_1 \cap \Ccal_2$ contains exactly one element $\gamma^* = P_{\Ccal_1 \cap \Ccal_2}(\gamma^0)$.
\end{lemma}

>>>>

As illustrated in Figure \ref{alternate_projections} (a-b), the Sinkhorn algorithm, that  realizes alternate Bregman projections onto the affine sets $\Ccal_1$ and $\Ccal_2$, can be very slow when $\epsilon\to 0$. The idea developped in this paper is to realize over-relaxed projections in order to accelerate the process, as displayed in Figure \ref{alternate_projections} (c)

\begin{figure}[ht!]
\begin{center}
\begin{tabular}{ccc}
%\includegraphics[width=3cm]{}&\includegraphics[width=3cm]{}&\includegraphics[width=3cm]{}\\
&TODO: mettre les figures du beamer\\
&en remplacant les $x$ par des $\gamma$\\
(a)&(b)&(c)
\end{tabular}
\caption{\label{alternate_projections} The trajectory of $\gamma^l$ given by the Sinkhorn algorithm is illustrated for decreasing values of $\epsilon$ in (a) and (b). In order to accelerate the convergence rate, over-relaxed projections are here considered (c).}
\end{center}
\end{figure}
\subsection{Over-relaxed projections}

@@

\begin{lemma}[{\color{red} Mettre la ref d'un papier de Marco}]
	\label{lemma:trivial_intersection}
	Let us take $\gamma^0$ in $\IR_{+*}^{n_1 n_2}$,
	and denote
	\[
	S = \left\{
	\diag(a) \gamma^0 \diag(b),\quad
	(a,b) \in \IR_{+*}^{n_1 + n_2}
	\right\}
	\]
	the set of matrices that are diagonally similar to $\gamma^0$.
	Then the set $S \cap \Ccal_1 \cap \Ccal_2$ contains exactly one element $\gamma^* = P_{\Ccal_1 \cap \Ccal_2}(\gamma^0)$.
\end{lemma}
